### 2011-02-10 Text/paper.tex
Added one profile. The diagonal number doesn't look too bad.

One can see the phase profile in the middle of the bubble in
Fig.\ref{fig:quarter:capillary:capillary01}. The associated capillary number is $0.053$ based on
the calculation of the bubble velocity in the center of the bubble. The radiuses are as follows:
$R_{axis}=0.99$ and $R_{diag}=1.400$. While th  
1.4000714267

\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/}
\end{figure}

@@

\section{Steady-state case}
We performed different simulations to understand a number of steps required for the problem to come
on the steady-state. The grid to be simulated is $52\mathrm{x}52\mathrm{x}750$ with the initial
width as $6.5$ lattice Boltzmann units together with $\frac{\mathrm{d}P}{\mathrm{d}x}=3
\mathrm{x}10^{-5}$. The simulation was performed for $200000$,$400000$,$600000$ and $800000$ time
iterations. The results are summarised in Table \ref{table:steady:state}. One of the profiles in
the middle of the bubble is shown in Fig. \ref{fig:steady:state:profile:example}.
\begin{table}
\begin{tabular}{|c|c|c|c|}
$N_{iter}$&$Ca$&$R_{axis}$&$R_{diag}$\\
$200000$&$0.285$&$0.873$&$0.921$\\
$400000$&$0.274$&$0.873$&$0.920$\\
$600000$&$0.263$&$0.872$&$0.919$\\
$800000$&$0.252$&$0.873$&$0.917$\\
\end{tabular}
\caption{Results for the steady-state case. One can see that $200000$ steps are enough to structure
the bubble. However, the interface is underresolved. That could be the influence of the bubble
length.\label{table:steady:state}}
\end{table}
\begin{figure}
\includegraphics[width=0.47\textwidth]{Figures/bullet.eps}\hfill
\includegraphics[width=0.47\textwidth]{Figures/example_crossection.eps}\\
\caption{Slice in the middle of the bubble and
three-dimensional example. \label{fig:steady:state:profile:example}}
\end{figure}

>>>>

One can see the phase profile in the middle of the bubble in
Fig.\ref{fig:quarter:capillary:capillary01}. The associated capillary number is $0.053$ based on
the calculation of the bubble velocity in the center of the bubble. The radiuses in this simulation
are as $R_{axis}=0.93$ and $R_{diag}=1.06$. While $R_{axis}=0.93$ is underestimated parameter and
we can't take into the consideration apriori, one can consider parameter $R_{diag}=1.06$ the
parameters for the capillary number $0.053$ should be according to \citet{heil-threedim} as $0.97$
and $1.05$ according to the VOF simulations of \citet{wang-non-circular}. One can conclude that
even though the axis film thickness is not properly resolved the diagonal values are consistent and
can give an approximate information. 
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/quarter.eps}\\ %\hfill
\includegraphics[width=0.97\textwidth]{Figures/stream_cap01.eps}\\
\caption{Streamlines and phase profile of the quarter of the channel. The capillary number is
$0.053$ and the film thickness is underresolved. \label{fig:quarter:capillary:capillary01}}
\end{figure}
{\color{red} Add more data here either with better grid or with the less velocity that we can
track the numbers.}

@@

\section{Steady-state case}
phase140000.vts
679 1225
952
Shape[1]= 52
46.8951843799
38.0090192997
Velx 1.83514289361e-07
Vely 1.83514289434e-07
Velz 0.0030119820173
0.937903687597 1.07505741172
Capillary= 0.0532448227311
phase150000.vts
693 1240
966
Shape[1]= 52
46.8788857523
37.9120765245
Velx 1.69288494763e-07
Vely 1.69288494735e-07
Velz 0.00302054511694
0.937577715046 1.07231545597
Capillary= 0.0533961983767
phase160000.vts
707 1255
981
Shape[1]= 52
46.8620677255
37.8057241388
Velx 1.52729098327e-07
Vely 1.52729098372e-07
Velz 0.00302874387384
0.93724135451 1.06930735625
Capillary= 0.0535411332917
phase170000.vts
721 1269
995
Shape[1]= 52
46.8470974943
37.699205304
Velx 1.36013430193e-07
Vely 1.36013430134e-07
Velz 0.00303548291501
0.936941949886 1.06629454863
Capillary= 0.0536602638346
phase180000.vts
735 1284
1009
Shape[1]= 52
46.8329488966
37.5823654668
Velx 1.20677254065e-07
Vely 1.20677254023e-07
Velz 0.00304140201352
0.936658977932 1.06298981898
Capillary= 0.0537648997019

We performed different simulations to understand a number of steps required for the problem to come
on the steady-state. The grid to be simulated is $52\mathrm{x}52\mathrm{x}750$ with the initial
width as $6.5$ lattice Boltzmann units together with $\frac{\mathrm{d}P}{\mathrm{d}x}=3
\mathrm{x}10^{-5}$. The simulation was performed for $200000$,$400000$,$600000$ and $800000$ time
iterations. The results are summarised in Table \ref{table:steady:state}. One of the profiles in
the middle of the bubble is shown in Fig. \ref{fig:steady:state:profile:example}.
\begin{table}
\begin{tabular}{|c|c|c|c|}
$N_{iter}$&$Ca$&$R_{axis}$&$R_{diag}$\\
$200000$&$0.285$&$0.873$&$0.921$\\
$400000$&$0.274$&$0.873$&$0.920$\\
$600000$&$0.263$&$0.872$&$0.919$\\
$800000$&$0.252$&$0.873$&$0.917$\\
\end{tabular}
\caption{Results for the steady-state case. One can see that $200000$ steps are enough to structure
the bubble. However, the interface is underresolved. That could be the influence of the bubble
length.\label{table:steady:state}}
\end{table}
\begin{figure}
\includegraphics[width=0.47\textwidth]{Figures/bullet.eps}\hfill
\includegraphics[width=0.47\textwidth]{Figures/example_crossection.eps}\\
\caption{Slice in the middle of the bubble and
three-dimensional example. \label{fig:steady:state:profile:example}}
\end{figure}
